Standard Deviation Outcome Change - DEVELOPMENT

### 2023-04-27 minos/outcomes/standard_deviation_change_SF12.Rmd
Functionalised the marginal density densigram plots, and created a new utils script for outcome visualisation functions

@@

```{r}

```

>>>>

```{r}
# FUNCTION
SF12_marg_dist_denigram_plot <- function(base, 
                                         int, 
                                         int.name, 
                                         target.year = 2035,
                                         save = FALSE,
                                         path = '/home/luke/Documents/WORK/MINOS/TEST_PLOTS/') {
  # get just one year
  b.start <- base %>% filter(time == 2020, SF_12 != -8.0)
  b.end <- base %>% filter(time == target.year, SF_12 != -8.0)
  i.end <- int %>% filter(time == target.year, SF_12 != -8.0)
  # get just the SF12 columns and rename for later
  b.start <- b.start %>% select(pidp, SF_12) %>% rename(initial = SF_12)
  b.end <- b.end %>% select(pidp, SF_12) %>% rename(end = SF_12)
  i.end <- i.end %>% select(pidp, SF_12) %>% rename(end = SF_12)

  # combine before we plot
  b.end$scen <- 'baseline'
  i.end$scen <- int.name
  combined <- rbind(b.end, i.end)

  # now merge with initial
  merged <- merge(b.start, combined, by = 'pidp')

  p <- ggplot(data = merged, aes(x = initial, y = end, group = scen, color = scen)) +
    geom_point(alpha = 0.6, size=0.1) +
    geom_smooth() +
    theme(legend.position = c(0.15, 0.9))

  p1 <- ggMarginal(p, type='densigram', groupColour = TRUE, xparams = list(position = 'dodge'), yparams=list(position = 'dodge'))
  p1

  plot.name <- paste0('scatter_marg_densigram_', int.name, '.png')

  if(save) {
    ggsave(filename = plot.name,
           plot = p1,
           path = path)
  }

  print(p1)

  return(p1)
}
```

@@

```{r}
# Test out the new function above
base <- read_singular_local_out(out.path, 'baseline')
livWage <- read_singular_local_out(out.path, 'livingWageIntervention')
energy <- read_singular_local_out(out.path, 'energyDownlift')
poverty <- read_singular_local_out(out.path, 'hhIncomePovertyLineChildUplift')
allchild <- read_singular_local_out(out.path, 'hhIncomeChildUplift')
```

```{r}
p.livWage <- SF12_marg_dist_denigram_plot(base, 
                                        livWage, 
                                        int.name = 'Living Wage',
                                        target.year = 2030,
                                        save=TRUE)
p.energy <- SF12_marg_dist_denigram_plot(base, 
                                        energy, 
                                        int.name = 'Energy Downlift',
                                        target.year = 2030,
                                        save=TRUE)
p.poverty <- SF12_marg_dist_denigram_plot(base, 
                                        poverty, 
                                        int.name = 'Poverty Child Uplift',
                                        target.year = 2030,
                                        save=TRUE)
p.allchild <- SF12_marg_dist_denigram_plot(base, 
                                        allchild, 
                                        int.name = 'Child Uplift',
                                        target.year = 2030,
                                        save=TRUE)
```
